---
title: "Design and analysis of Photonic Crystal Fiber (PCF) based optical sensor"
author: Nazmul Hossen
output: powerpoint_presentation
date: "2023-03-16"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Outlines
- Introduction to PCF
- How data are generated
- Different statistical tests


## Photonic Crystal Fiber (PCF)

- A kind of optical fiber that uses photonic crystals to form the cladding around the core of the cable.


- A low-loss periodic dielectric medium constructed using a periodic array of microscopic air holes that run along the entire fiber length. 

- Light travels through the core using the refraction property of light, which occurs because of the difference between the refractive indices of the core and cladding.

- Use total internal reflection or light confinement in hollow core methods to propagate light

![Basic PCF structure (https://www.techopedia.com)](C:/Users/nazmul_hossen/Usask/STAT 834 (winter)/project/PCF.png)

## Designed PCF

![Figure: designed PCF structure](C:/Users/nazmul_hossen/Usask/STAT 834 (winter)/project/PCF-sensor-diagram.png)

## Simulation tool
![Comsol multiphysics (https://www.comsol.com)](C:/Users/nazmul_hossen/Usask/STAT 834 (winter)/project/Comsol.png)

## Slide with R Output



summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

